%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
\usepackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\setmainfont{Latin Modern Sans}


% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ydnt, maxbibnames=5]{biblatex}


%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

\DeclareNameAlias{sortname}{given-family}
\DeclareNameAlias{default}{given-family}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

\newenvironment{job}[2]
{
	\begin{tabularx}{\linewidth}{@{}l X r@{}}
		\small
		\textbf{#1} & \hfill &  #2 \\[3.75pt]
	\end{tabularx}
	\footnotesize
	\setlength{\parskip}{3pt} % spacing between paragraphs
	\setlength{\parindent}{0pt} % no indentation
}
{
}


\usepackage{enumitem}

% Define compact list styles
\setlist[itemize,1]{nosep,after=\strut, leftmargin=2em, itemsep=3pt, label=•}
\setlist[itemize,2]{nosep,after=\strut, leftmargin=2em, itemsep=2pt, label=$\circ$}



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Dimitris Tsitsigkos} \\[7.5pt]
\Large{Software Engineer (PhD)} \\[7.5pt]

\href{https://gr.linkedin.com/in/dimitris-tsitsigkos}{\raisebox{-0.05\height}\faLinkedin\ dtsitsigkos} \ $|$ \ 
\href{https://dtsitsigkos.github.io/}{\raisebox{-0.05\height}\faGlobe \ dtsitsigkos.github.io} \ $|$ \  
\href{https://dblp.org/pid/163/0537.html}{\raisebox{-0.05\height}\faDatabase\ DBLP}  \ $|$ \ 
\href{https://scholar.google.com/citations?user=z_KVU0QAAAAJ}{\raisebox{-0.05\height}\faGraduationCap\ Google Scholar}\ $|$ \
\href{https://github.com/dTsitsigkos}{\raisebox{-0.05\height}\faGithub\ dtsitsigkos} \ 

\href{mailto:tsitsigkosdim@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ tsitsigkosdim@gmail.com} \ $|$ \
\href{tel:+30 6942951698}{\raisebox{-0.05\height}\faMobile \ +30 6942951698}
 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
 %\small Postdoctoral Researcher and Software Engineer with extensive experience in data management, including indexing, query optimization, and query processing. Skilled in developing efficient indices for parallel processing of relational, spatial, and multi-dimensional data. Experienced in designing and implementing research-based software frameworks. Strong collaborator with excellent communication skills, bridging research insights and practical software engineering solutions.
%\small Research software engineer focused on data systems, performance, and parallel computing. Strong background in relational and spatial data processing, query optimization, and large-scale system design. Experienced in C++, Java, and Python, creating algorithms and frameworks for high-performance data systems. Passionate about efficient code, reliability, and building solid data infrastructure. add something about the future...
%\small Software engineer and researcher focused on data management and parallel computing. Strong background in relational and spatial data processing, query optimization, and large-scale system design. Experienced in C++, Java, and Python, developing algorithms and frameworks for high-performance data systems. Looking to work in a challenging environment where I can apply my expertise and continue building my technical skills as part of an engineering team.

\small Software Engineer with a background in data management and parallel computing. Experienced in the design and implementation of in-memory indexing techniques that accelerate query performance for single and multi-dimensional data. Focuses on developing scalable data systems and performance-critical algorithms in C++, Java, and Python, leveraging parallelism and memory-efficient designs to solve complex data challenges.

%----------------------------------------------------------------------------------------
%	Technical Skills
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
	Languages: &  \normalsize{C, C++, Java, Python
	}\\
	Data Management:  &  \normalsize{MySQL, PostgreSQL, PostGIS, HBase}\\ 
	Parallel \& Systems Programming: &  \normalsize{OpenMP, SIMD, MPI}\\
	Distributed Data Frameworks:&  \normalsize{Hadoop, Spark, Dask}\\
	Web \& Frameworks: &  \normalsize{Spring, RESTful Web Services, JavaScript, JSP, JSF
	}\\
	Operating Systems: &  \normalsize{Ubuntu, Microsoft Windows, macOS
	}\\   
\end{tabularx}


%Experience
\section{Work Experience}

%\begin{jobshort}{\href{https://archimedesai.gr/en/}{ARCHIMEDES} unit of Athena Research Center, Athens}{February 2025 - present}
%Postdoctoral Researcher
%\item Member of the data science team, focusing on multi-dimensional and vector data.
%\end{jobshort}

\begin{job}{\href{https://archimedesai.gr/en/}{Archimedes} Research on AI, Data Science and Algorithms, Greece}{Feb 2025 - present\phantom{Ja}}	
\textbf{Research Engineer} (\href{https://archimedesai.gr/en/research/research-areas/data-science-and-engineering}{Data Science and Engineering team})

\begin{itemize}

\item Developed performance-critical indexing components for multi-dimensional and vector data, focusing on low-latency query execution.

\item Implemented and optimized in-memory data structures using C++, leveraging multi-core parallelism (OpenMP) and SIMD to improve query throughput.

\item Worked on hardware-aware optimizations and memory-efficient designs to scale query processing on modern multi-core systems.
\item \underline{Technologies:} \textbf{C++, openMP, SIMD}.
\end{itemize}

\end{job}


\begin{job}{\href{https://www.cse.uoi.gr/?lang=en}{Dept. of Computer Science \& Engineering}, Univ. of Ioannina, Greece}{Jan 2024 – Dec 2024}
	\textbf{Software Engineer (PhD Research)}
	\begin{itemize}
		
		\item Implemented novel parallel and non-parallel index structures in C++ for spatial queries, including spatial join, range queries, and k-NN.
		
		\item Designed memory-efficient algorithms and data partitioning strategies to scale query processing on multi-core architectures.
		
		\item Contributed to the design and development of a prototype distributed spatial data management system using MPI and OpenMP, focusing on scalability and performance.
		
		\item \underline{Technologies:} \textbf{C++, OpenMP, MPI}.
		
	\end{itemize}
	
\end{job}

\vspace{-1\baselineskip}

\begin{job}{\href{https://www.imsi.athenarc.gr/en}{Information Management Systems Institute}, Athens, Greece}{Dec 2012 – Dec 2023}
\textbf{Software Engineer}

Participated in several Greek and European funding projects, including:
	\begin{itemize}
		
		\item \href{https://www.more2020.eu/}{MORE}: Management of Real-time Energy data.
		
		(Oct 2020 – Dec 2023)		
		\begin{itemize}
			\item Developed a parallel continuous evaluation module in Java for sliding-window aggregations to process real-time sensor data at the edge, enabling faster response times for energy analytics workloads.
			\item Implemented parallel and distributed data processing pipelines in Python using Dask to improve the efficiency and scalability of large-scale time-series analytics.
			\item \underline{Technologies:} \textbf{Java, Python, Dask}.
		\end{itemize}
		
			
		\item \href{https://amnesia.openaire.eu/}{Amnesia}: A platform for anonymizing relational, multi-dimensional, and hierarchical data.
		
		(Aug 2015 – Sep 2020)
		\begin{itemize}
			\item Led the end-to-end design and development of a open-source data anonymization platform, providing high-performance privacy guarantees for complex datasets.
			\item Developed the core anonymization engine in Java, implementing efficient algorithms to process large-scale data transformations with minimal information loss.
			\item Designed and implemented RESTful APIs using Spring, and integrated the platform into the \href{https://www.openaire.eu/}{OpenAIRE}  ecosystem, supporting a global community of researchers and data providers.
			\item Owned the full software development lifecycle, including requirements analysis, system design, implementation, and deployment.
			
			\item \underline{Technologies:} \textbf{Java, Spring, RESTful Web Services, JavaScript}.
			
		\end{itemize}
		
		\vspace{-1\baselineskip}
		
		\item \href{http://www.modissense.gr/}{MoDisSENSE}: A Distributed Spatio-Temporal and Textual Processing Platform for Social.
		
		(Dec 2012 - Jul 2015)
		\begin{itemize}
			\item Developed distributed data processing algorithms in Java using Hadoop and HBase to analyze large-scale location data, including point-of-interest discovery and trajectory reconstruction from GPS traces.
			\item Built backend services and RESTful APIs in Java, backed by PostgreSQL, to support spatial data processing and recommendation functionality.
			\item \underline{Technologies:} \textbf{Java, RESTful Web Services MapReduce, Hadoop, HBase, PostgreSQL}.
			
		\end{itemize}
		
	\end{itemize}
\end{job}

\vspace{-2\baselineskip}

\begin{job}{\href{https://www.informatik.uni-mainz.de/en/}{Institute of CS}, Johannes Gutenberg University Mainz, Germany}{May 2022 – Jul 2022}
	\textbf{Visiting Researcher (PhD Collaboration)}
	
	\begin{itemize}
		
		\item Implemented and optimized spatial join algorithms in C++, focusing on performance and memory efficiency.
		
		\item \underline{Technologies:} \textbf{C++ and OpenMP}.
	\end{itemize}
	
\end{job}



\begin{job}{Hellenic Army Information Technology Support Center, Greece}{Apr 2017 – Nov 2018}
\textbf{Software Engineer}
	
	\begin{itemize}
		
		\item Maintained and extended backend Java applications, implementing new features and resolving production issues for internal information systems.
		
		\item Worked with Oracle Database to support application data storage and retrieval.
		
		\item Optimized database queries and backend logic to improve the performance of internal information systems.
		
		\item \underline{Technologies:} \textbf{Java, Oracle Database, JSF}.
	\end{itemize}
	
\end{job}




%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{job}{PhD, Computer Science}{Jul 2019 – Dec 2024}
	Department of Computer Science \& Engineering, University of Ioannina (UoI)
	
	\underline{\textit{Thesis: In-memory Indexing for Parallel Processing of Single and Multi-Dimensional Queries}}
\end{job}

\vspace{-0.2\baselineskip}

\begin{job}{M.Sc., Computing Systems: Software and Hardware, Computer Science}{Nov 2012 – Sep 2016}
	Department of Informatics and Telecommunications, National and Kapodistrian University of Athens (NKUA)
	
	\underline{\textit{Thesis: Complex Event Processing (CEP) for Intrusion Detection}}	
\end{job}

\vspace{-0.2\baselineskip}

\begin{job}{B.Sc., Computer Science}{Sep 2006 – Jun 2012}
	Department of Informatics and Telecommunications, National and Kapodistrian University of Athens (NKUA)
	
	\underline{\textit{Thesis: Clustering Wikipedia resources}}
\end{job}




%----------------------------------------------------------------------------------------
%	Awards
%----------------------------------------------------------------------------------------


\section{Awards}

\begin{job}{3rd place \href{https://databasecontest2024.athenarc.gr/}{Future of Database Programming Contest}, Athens} {Mar 2025}
		
\end{job}







%----------------------------------------------------------------------------------------
%	Professional Activities 
%----------------------------------------------------------------------------------------
%\section{Academic Service}
%\begin{tabularx}{\linewidth}{@{}l X@{}}
%	Member of Program Committee
%	 &  \normalsize{TSAS 2023, ICDE 2026, IEEE BigData 2025
%	}\\
	
	
%	External Reviewer
%	  &  \normalsize{ICDE 2019-2025, VLDB 2019-2023, SIGMOD 2020, SIGSPATIAL 2020-2023, EDBT 2021-2025, ICDM 2025
%	  }\\ 
%\end{tabularx}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------



\section{Selected Publications}


\begin{refsection}[citations.bib]
	\setlength\bibitemsep{0.5em}
	\nocite{*}
	\printbibliography[heading=none]
\end{refsection}


%----------------------------------------------------------------------------------------
%	Other
%----------------------------------------------------------------------------------------

%\vspace{-0.4 cm}
\section{Other}
%\vspace{0.2\baselineskip}
\begin{tabularx}{\linewidth}{@{}l X@{}}
	Languages
	&  \normalsize{Greek (native), English (Advanced)	}\\
	
	
	
	%Awards
	%&  \normalsize{3rd place - \href{https://databasecontest2024.athenarc.gr/}{Future of Database Programming Contest} (March 2025, Athens).
	%}\\ 
	
	Volunteer	&  \normalsize{European Data Forum 2014, EDBT/ICDT 2023 Joint Conference, 6th ACM Europe Summer School on Data Science 2025, HDMS 2025.
		
	}\\ 
\end{tabularx}


\end{document}
